pSEOBNRv4HM

### 2020-10-27 papers/intro_paper/intro_paper.tex
updated paper

@@

To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger \abhi{be more specific}, and differ in their post-merger description. We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $d\omega =d\tau = 0.5$. In other words, we assume that the frequency and damping time of our nonGR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}). We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. The posterior probability distributions on $\{d\omega,d\tau\}$ or equivalently$(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ (dashed lines in Fig.\ref{fig:gr_simulation})) are consistent with the corresponding the values of the injection parameters, indicated by plus signs \abhi{add markers in effective quantity plots}.

@@

\subsection{Simulations using NR signals}

@@

\abhi{A comparison with pyRING}
\abhi{damped sinusoid results}

>>>>

\subsubsection{Test of the No hair theorem}

We provide a simple demonstration of a test of the no-hair theorem using our model. As described in the introduction, any test of the no-hair theorem of black holes would need to involve the independent measurements of (at least) two different QNMs. We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning binary black hole with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$. We choose an asymmetric system to increase the SNR in the higher modes. We also rescale the distance and orientation of the binary such that the total SNR of the signal is 75. Based on the LIGO-Virgo observations during  O3, such asymmetric and loud signals are no longer just a theoretical prediction but quite the possibility at design sensitivities CITE of these detectors. Using the signal, we attempt to measure the QNM frequencies corresponding to the zeroeth overtone of the $(2,\pm 2)$ and $(3,\pm 3)$ modes~\ref{fig:nohair_sxs}. We explore two cases, where we fix either one of the $(2,\pm 2)$ or $(3,\pm 3)$ frequency and damping time, ie, $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ or $(f_{330}^{\text{eff}}, \tau _{330}^{\text{eff}})$ fixed at their GR predictions and estimating the other pair.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
	%\includegraphics[width=0.3\textwidth]{figures/GW150914_GW190521_simulated_frac.png}\includegraphics[width=0.56\textwidth]{figures/GW150914_GW190521_simulated_abs.png}
	\label{fig:nohair_sxs}
	\caption{SXS:BBH:0166. 220/330 measurement}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

To demonstrate the robustness of the method in detecting possible deviations of the underlying GW signal from predictions of GR, we inject simulated GW signals which are identical to the corresponding GR prediction upto merger \abhi{be more specific}, and differ in their post-merger description. We again choose systems with initial-binary-parameters similar to GW150914 and GW190521, but we attach a phenomenological post-merger signal described by deviation parameters $d\omega =d\tau = 0.5$. In other words, we assume that the frequency and damping time of our nonGR signal is 1.5 times the corresponding GR prediction, although the pre-merger signal is identical to GR (Fig.\ref{fig:nongr_waveform}). We also avoid waveform and noise systematic biases by choosing a configuration identical to the simulations described in Sec.\ref{ssec:gr_signal}. The posterior probability distributions on $\{d\omega,d\tau\}$ or equivalently $(f_{220}^{\text{eff}}, \tau _{220}^{\text{eff}})$ (dashed lines in Fig.\ref{fig:gr_simulation})) are consistent with the corresponding the values of the injection parameters, indicated by plus signs \abhi{add markers in effective quantity plots}.

@@

@@

\iffalse
\abhi{A comparison with pyRING}
\abhi{damped sinusoid results}
\fi
